---
title: "Semantix Challenge - First Part"
author: "Rui Romanini"
date: "10 de novembro de 2016"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

In this challenge, suppose we are looking to do social network
analysis for prospective customers. We want to extract from
their social network a metric called "closeness centrality".

Centrality metrics try to approximate a measure of influence
of an individual within a social network. The distance between
any two vertices is their shortest path. The *farness*
of a given vertex *v* is the sum of all distances from each vertex
to *v*. Finally, the *closeness* of a vertex *v* is the inverse
of the *farness*.

The first part of the challenge is to rank the vertices in a given
graph by their *closeness*. The graph is provided in the attached
file; each line of the file consists of two vertex names separated by a single space, representing an edge between those two nodes.

##The environment
It's important to pay atention to the environment, to make sure about reproducibility. 

This code was produced using R version 3.3.1 and R Studio version 0.99.489

The Operational System it's Windows 10 Home

##Reading the graph

In this step, the edges.dat file it's downloaded from the GitHub Repository and the vertices are read using read.csv function.
Blank space used as separator and there is no Header in this file.
Only two columns representing the vertices and the edge.


```{r}
vertices <- read.csv("C:\\Rui\\Data Science\\teste\\edges.dat" ,sep = " ",header = FALSE)
```

##Creating the graph from the data frame

Now we can build the net from the vertices

```{r}
install.packages("igraph", repos = "http://cran.us.r-project.org")
library(igraph)
```

```{r}
net <-graph_from_data_frame(d=vertices,directed = T)
```


##Creating the plot

Now we can build the plot showing the nodes and connections

```{r}
l <- layout_with_fr(net)
l <- norm_coords(l, ymin=-1, ymax=1, xmin=-1, xmax=1)

plot(net,edge.arrow.size=.05,vertex.size=10,
     edge.curved=0.2,
     vertex.frame.color="black",
     vertex.color="green",
     vertex.label.cex=0.5,rescale=F, layout=l*1.2)
```

##Getting the Closeness

Now we can build the closeness

```{r}
closeness(net, mode="all", weights=NA)
centr_clo(net, mode="all", normalized=T)
```


##Resume

Now we can build the closeness
